### 2021-03-03 ch01_introduction/introduction.tex
Restructured thesis and removed unnecessary parts

%=============================================================================%
%                                Dissertation                                 %
%                               Manuel Schlund                                %
%                                  (c) 2020                                   %
%=============================================================================%
%                                Introduction                                 %
%=============================================================================%

@@

Parts of this thesis are already published in multiple peer-reviewed
publications (two first-author studies and six co-author studies). Wherever
material from these studies is presented in this thesis, the pronoun
\enquote{we} is used to increase readability by avoiding the passive voice and
to acknowledge all involved contributors. However, unless stated otherwise, all
contents from these publications (text, figures and tables) shown in this
thesis originate from the author of this thesis. A detailed list of
contributions to these studies (including their full reference) is given in the
corresponding \namecrefs{ch:03:esmvaltool}.

>>>>

%=============================================================================%
%                            Doctoral Dissertation                            %
%                               Manuel Schlund                                %
%                                  (c) 2021                                   %
%=============================================================================%
%                                Introduction                                 %
%=============================================================================%

@@

Parts of this thesis are already published in multiple peer-reviewed
publications (two first-author studies and six co-author studies). A complete
list of these is given on \cpageref{ch:bib:own}. Wherever material from these
studies is presented in this thesis, the pronoun \enquote{we} is used to
increase readability by avoiding the passive voice and to acknowledge all
involved contributors. However, unless stated otherwise, all contents from
these publications (text, figures and tables) shown in this thesis originate
from the author of this thesis. A detailed list of contributions to these
studies (including their full reference) is given in the corresponding
\namecrefs{ch:03:esmvaltool}.
